---
title: "Codebook for 'Average of Mean and Standard Deviation of Activity Measurement' Dataset"
output: html_document
---

```{r, echo=FALSE}
d <- Sys.Date()
```
**Date Created:** `r d`

Codebook prepared by Sandhya Raghavan based on a tidy dataset created for Average of Activity measurment. The dataset was prepared by cleansing the data collected from the accelerometers from the Samsung Galaxy S smartphone.

Below is the link to the ReadMe file of the cleansing procedure followed.
## ADD LINK HERE

The **Average_of_Mean_and_STD_of_Activity_Measurment.txt** contains total of 180 records for 30 subjects (identified by subject_id) across 6 differnet Activities.The activities are as follows:

```{r, echo=FALSE}
act  <- paste(c("WALKING","WALKING_UPSTAIRS","WALKING_DOWNSTAIRS","SITTING","STANDING","LAYING"),sep = "\n")
```
`r act`

Below is the definition for the other variables in the dataset:

```{r , echo=FALSE}
data <- read.csv("data/Average_of_Activity_Measurment.csv")
code_book <- data.frame(Variable_Name=c(names(data)))
st <- sapply(data,class)
code_book$Variable_Type <- st[code_book$Variable_Name]
code_book$Unit_of_Measurment <-  c("HZ")
code_book[c(1,2),3] <- c("N/A")
code_book$Column_Position <- seq(along=code_book$Variable_Name)
library(knitr)
kable(code_book)
```

## Appendix

R Snippet used to create code book is below
```{r , results="hide"}
## Stored onemore tidy data set as csv just for convenience
data <- read.csv("data/Average_of_Activity_Measurment.csv")
code_book <- data.frame(Variable_Name=c(names(data)))
st <- sapply(data,class)
code_book$Variable_Type <- st[code_book$Variable_Name]
##code_book$Variable_Description <-  code_book$Variable_Name
code_book$Column_Position <- seq(along=code_book$Variable_Name)
library(knitr)
kable(code_book)
```
